---
title: "HiTS-EQ"
author: "Hsuan-Chun Lin"
date: "November 2, 2018"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)
```

## HiTS-EQ
This is the document for calculation of more than 4000 association constants from HiTS-EQ Next generation sequencing dataset.

1. Input your data. The data format is in .csv file and the csv file format is shown below.
```{r }
#Data input
test.import <- read.csv('import_data.csv', header=T)
head(test.import)
```
Here f means fraction of reaction and the 100% binding is 1. 0.5 means 50% E-S complex formation or [ES]/[S]) = 0.5.

```{r echo=FALSE}
test <- test.import[-(1:2),]
frac <- 1-as.numeric(test.import[1,2:5])
Enzyme <- as.numeric(test.import[2,2:5])
names(test)<-c("sequence","t0","t1","t2","t3")
#calculate the summation and mole fraction
sum <- apply(test[,2:5],2,sum)
test$ft0 <- test$t0/sum[1]
test$ft1 <- test$t1/sum[2]
test$ft2 <- test$t2/sum[3]
test$ft3 <- test$t3/sum[4]

#calculate the fraction of individual substrate
test$fr0 <- 1-test$ft0/test$ft0*frac[1]
test$fr1 <- 1-test$ft1/test$ft0*frac[2]
test$fr2 <- 1-test$ft2/test$ft0*frac[3]
test$fr3 <- 1-test$ft3/test$ft0*frac[4]

#convert negative to random small amount in test

for(i in 1:length(test[,1])){
  for(j in 10:13){
   if(test[i,j] < 0){
     test[i,j] <- abs(rnorm(1,0)/100)
   } 
  }
}

#fitting
test$K <- 0

for (i in 1:length(test[,1])){
  data.ft <- cbind(Enzyme,t(test[i,10:13]))
  data.ft <- data.frame(data.ft)
  names(data.ft) <- c("Enzyme","f")
  dirf <- nls( f ~ Enzyme/(Enzyme + K), data = data.ft)
  test$K[i] <- coef(dirf)
#Export final result  
finalresult <- test[,c("sequence","K")]
finalresult$KA <- 1/finalresult$K
finalresult$RKA <- finalresult$KA/finalresult$KA[3]
}
```
##Result output

After fitting, the association constant (KA), dissociation constant (K), and relative association constant (RKA) will be exported in the following format. 
```{r }
head(finalresult)
```
To export your file, please change the export filename in HiTS-EQ_v2.R script.
```{r }
write.csv(finalresult,"output.csv")
```
## Show the RKA distribution by histogram
To observe the distribution of relative association constants, we used RKA and log(RKA). log(RKA) has more physical meanings in binding energy.

```{r }
hist(finalresult$RKA)
```

```{r }
hist(log(finalresult$RKA))
```
